\documentclass[a4paper, 10pt]{article}
    \usepackage[subpreambles=true]{standalone}
    \usepackage[english, american, british]{babel}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \usepackage{hyphenat}
    \hyphenation{Mathe-matik wieder-gewinnen}
    \usepackage{amsmath}
    \usepackage{import}
    \usepackage{tabularx}
    \usepackage{graphicx}
    \usepackage[margin=2cm ]{geometry}

    \title{Einführung in die Softwaretechnik 2018 \\ Sheet 05}
    \author{Maximilian Frühauf}

\begin{document}
\maketitle
\begin{enumerate}
    \item
    Explain the difference between a 3-layered architectural style and a 3-tier architecture.
    \vspace{0.5cm}

    A 3-layered architecture is a system that has 3 hierarchically ordered layers in the model.
    A 3-tier architecture however is also divided into three separate layers, but these are then 
    distributed to three different physical systems.
    \item
    Create a UML component diagram for Bumpers based on the following analysis object model. 
    Use the Model View Controller (MVC) architectural style and explain why you modeled it like this.
    \vspace{0.5cm}
    \item
    Consider the following extension to Bumpers. 
    The game includes a high- score mechanism to determine the best players. 
    High-scores are saved on a separate database server and are accessed by the game through an 
    application server. To improve redundancy, two identical database servers should be used: 
    the first acts as a main server, and the second acts as a redundant back-up in case the 
    first one fails. The Bumpers game accesses data through the application server. 
    Game administrators have the option of using a proprietary client that accesses the databases 
    directly. Draw a UML deployment diagram representing the hardware/ software mapping of this 
    system and explain why you modeled it like this. Which architectural style did you choose?
    \vspace{0.5cm}
    \item
    Consider a legacy, fax-based, problem-reporting system for an aircraft manufacturer. 
    You are part of a reengineering project replacing the core of the system with a 
    computer-based system that includes a database and a notification system. 
    The client requires the fax to remain an entry point for problem reports. 
    You propose an E- mail entry point. Describe a subsystem decomposition that would allow 
    both interfaces. Note that such systems are used to process many problem reports per 
    day (e.g., 2000 faxes per day). Draw a UML component diagram representing the 
    subsystem decomposition of this system and explain why you modeled it like this.
    \vspace{0.5cm}
\end{enumerate}
\end{document}